Bayesian Hierarchical Modeling: An Introduction and Reassessment

### 2023-06-29 E - Tutorial Log-Normal Model Rstan/Online Supplement E - Bayesian Hierarchical Modeling in rstan - Log Model.Rmd
Updates cor model

|  The stan file `myLogModel.stan` is used to fit the full model and can be found under R objects > rstan > linear model. It contains descriptions for every line of code. The stan file is divided in three sections (in our case):

@@

\scriptsize 
```{r loadmodelfit, eval = FALSE}
logmodel_fit <- readRDS(file = "myPath/rstan_logmodel_fit.rds")
```
\normalsize 
```{r loadmodelfit2, echo = FALSE}
setwd('..')
logmodel_fit <- readRDS(file = "R objects/rstan/log-normal model/hier_logmodelc_adj13012022.rds")
```

>>>>

|  The stan file `myLogModel.stan` is used to fit the full model and can be found under K - R objects > rstan > linear model. It contains descriptions for every line of code. The stan file is divided in three sections (in our case):

@@

\scriptsize 
```{r loadmodelfit, eval = FALSE}
logmodel_fit <- readRDS(file = "myPath/rstan_logmodel_fit.rds")
```
\normalsize 
```{r loadmodelfit2, echo = FALSE}
setwd('..')
logmodel_fit <- readRDS(file = "K - R objects/rstan/log-normal model/hier_logmodelc_adj13012022.rds")
```

### 2023-06-29 F - Tutorial Log-Normal Model brms/Online Supplement F - Bayesian Hierarchical Modeling in brms - Log Model.Rmd
Updates cor model

\scriptsize 
```{r loadmodelfits, show = FALSE, echo = FALSE}
setwd('..')
logmodel_fit <- readRDS(file = "R objects/brms/log-normal/brmmodel8log13012022.rds")

# For model comparison - sample_prior was set to "yes" 
logmodel_fit_bf <- readRDS("R objects/brms/BF/brmmodel8log26052022_bf.rds")

>>>>

\scriptsize 
```{r loadmodelfits, show = FALSE, echo = FALSE}
setwd('..')
logmodel_fit <- readRDS(file = "K - R objects/brms/log-normal/brmmodel8log13012022.rds")

# For model comparison - sample_prior was set to "yes" 
logmodel_fit_bf <- readRDS("K - R objects/brms/BF/brmmodel8log26052022_bf.rds")

### 2023-06-29 H - Posterior Distributions Tables/Online Supplement H - Tables with Information on Posterior Distributions.Rmd
Updates cor model

## Normal model 
### Rstan 
\normalsize 
```{r loadmodelfit1, echo = FALSE}
setwd('..')
model_fit <- readRDS(file = "R objects/rstan/normal model/hier_modelc_adj_07012022.rds")
```

@@

### brms 
```{r loadmodelfits2, show = FALSE, echo = FALSE}
setwd('..')
model_fit <- readRDS(file = "R objects/brms/Truncated/BRMSmodelfit18_03012022.rds")

@@

## Log normal model 
### Rstan 
```{r loadmodelfit3, echo = FALSE}
setwd('..')
logmodel_fit <- readRDS(file = "R objects/rstan/log-normal model/hier_logmodelc_adj13012022.rds")
```

@@

\scriptsize 
```{r loadmodelfits4, show = FALSE, echo = FALSE}
# Log model brms 
setwd('..')
logmodel_fit <- readRDS(file = "R objects/brms/log-normal/brmmodel8log13012022.rds")

>>>>

## Normal model 
### Rstan 
\normalsize 
```{r loadmodelfit1, echo = FALSE}
setwd('..')
model_fit <- readRDS(file = "K - R objects/rstan/normal model/hier_modelc_adj_07012022.rds")
```

@@

### brms 
```{r loadmodelfits2, show = FALSE, echo = FALSE}
setwd('..')
model_fit <- readRDS(file = "K - R objects/brms/Truncated/BRMSmodelfit18_03012022.rds")

@@

## Log normal model 
### Rstan 
```{r loadmodelfit3, echo = FALSE}
setwd('..')
logmodel_fit <- readRDS(file = "K - R objects/rstan/log-normal model/hier_logmodelc_adj13012022.rds")
```

@@

\scriptsize 
```{r loadmodelfits4, show = FALSE, echo = FALSE}
# Log model brms 
setwd('..')
logmodel_fit <- readRDS(file = "K - R objects/brms/log-normal/brmmodel8log13012022.rds")
